---
title: "descriptive_visualizations"
author: "Hannah Schweren"
date: "2024-03-28"
output: html_document
---
This script turns descriptive insights and indicators in nicely interpretable tables


```{r}
library(legislatoR)
library(WikipediR)
library(rvest)
library(dplyr)
library(stringr)
library(ggplot2)
library(tm)
library(MatchIt)
library(quanteda)
library(purrr)
library(dplyr)
library(tidyverse)
library(rstatix)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(rstatix)
library(effsize)
library(kableExtra)
library(magick)
library(webshot2)
library(here)
library(scales)
library(corrplot)




```


```{r}
eu_political <- read.csv(here("data", "raw", "deu_political.csv"))
deu_traffic <- read.csv(here("data", "raw", "deu_traffic.csv"))
deu <- read.csv(here("data", "clean", "deu.csv"))
matched_data <- read.csv(here("data", "clean", "matched_data.csv"))


add_stars <- function(p_value) {
  if (p_value < 0.001) {
    return("***")
  } else if (p_value < 0.01) {
    return("**")
  } else if (p_value < 0.05) {
    return("*")
  } else {
    return("")
  }
}
```

Descriptive analyis of the text length of the unmatched sample - the data istransformed using a log2 scale to improve visibility while also allowing for an intuitive interpretation of the results. Specifically, an increase by one unit on the transformed scale corresponds to a doubling of the original value.

first for the unmatched data:

1.1. Text length
```{r}

#exclude cases where extracting did not work out properly
filtered_data_deu <- deu

#Ersetze Werte kleiner als 60 in text_length_live mit NA im neuen DataFrame
filtered_data_deu$text_length_live[filtered_data_deu$text_length_live < 60] <- NA
filtered_data_deu$text_length_career[filtered_data_deu$text_length_career < 60] <- NA


# Log2 transformation

filtered_data_deu$text_length_log2 <- log2(filtered_data_deu$text_length)


# calculate the p-value using a two-sample t-test
t_test_result <- t.test(text_length_log2 ~ sex, data = filtered_data_deu)


deu_text_length_2 <- ggplot(filtered_data_deu, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = text_length, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Text length (characters)", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')
  
  
deu_text_length_2

ggsave(here("visualisations", "deu_boxplot1.pdf"), plot = deu_text_length_2, width = 5, height = 6, units = "in", dpi = 600)

```

1.2. Text length life section
```{r warning=FALSE}
# Log2 transformation

#deu$text_length_life_log2 <- log2(deu$text_length_live)


# calculate the p-value using a two-sample t-test
#t_test_result <- t.test(text_length_life_log2 ~ sex, data = deu, na.action = na.exclude)



filtered_data_deu$text_length_life_log2 <- log2(filtered_data_deu$text_length_live)


# Führe den t-Test mit den transformierten Daten durch
t_test_result <- t.test(text_length_life_log2 ~ sex, data = filtered_data_deu, na.action = na.exclude)




deu_text_length_life_2 <- ggplot(filtered_data_deu, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = text_length_live, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
  scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Text length, life section (characters)", 
       caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + 
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), 
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), 
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, face = "bold"), 
    axis.title.y = element_text(size = 16, face = "bold"), 
    axis.text.x = element_text(size = 16), 
    axis.text.y = element_text(size = 13)  
  ) + 
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')

deu_text_length_life_2


ggsave(here("visualisations", "deu_boxplot2.pdf"), plot = deu_text_length_life_2, width = 5, height = 6, units = "in", dpi = 600)

```

1.3. Text length career section
```{r warning=FALSE}
# Log2 transformation

#deu$text_length_career_log2 <- log2(deu$text_length_career)


# calculate the p-value using a two-sample t-test
#t_test_result <- t.test(text_length_career_log2 ~ sex, data = deu, na.action = na.exclude)

#exclude cases where extracting did not work out properly
filtered_data_deu$text_length_career_log2 <- log2(filtered_data_deu$text_length_career)

# Führe den t-Test mit den transformierten Daten durch
t_test_result <- t.test(text_length_career_log2 ~ sex, data = filtered_data_deu, na.action = na.exclude)
# 


deu_text_length_career_2 <- ggplot(filtered_data_deu, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = text_length_career, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Text length, career section (characters)", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')


deu_text_length_career_2

ggsave(here("visualisations", "deu_boxplot3.pdf"), plot = deu_text_length_career_2, width = 5, height = 6, units = "in", dpi = 600)
```

1.4. Number of links
```{r}

deu$number_of_links_log2 <- log2(deu$number_of_links)

# p-Wert aus einem T-Test für die Anzahl der Links berechnen
t_test_result <- t.test(number_of_links_log2 ~ sex, data = deu)




deu_links_2 <- ggplot(deu, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = number_of_links, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Number of links", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE) + 
  scale_y_continuous(trans = 'log2')

deu_links_2

# Plot speichern
ggsave(here("visualisations", "deu_boxplot4.pdf"), plot = deu_links_2, width = 5, height = 6, units = "in", dpi = 600)
```

1.5. Number of page edits
```{r}

# Log2 Transformation
# 
 deu$total_edits_log2 <- log2(deu$total_edits)

t_test_result <- t.test(total_edits_log2 ~ sex, data = deu)



deu_edits_2 <- ggplot(deu, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = total_edits, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Number of edits", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
   theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) + 
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')


deu_edits_2

ggsave(here("visualisations", "deu_boxplot5.pdf"), plot = deu_edits_2, width = 5, height = 6, units = "in", dpi = 600)

```


And also for the matched data:

2.1. Text length
```{r}

# Log2 transformation

#exclude cases where extracting did not work out properly
filtered_data_matched <- matched_data

#Ersetze Werte kleiner als 60 in text_length_live mit NA im neuen DataFrame
filtered_data_matched$text_length_live[filtered_data_matched$text_length_live < 60] <- NA
filtered_data_matched$text_length_career[filtered_data_matched$text_length_career < 60] <- NA


filtered_data_matched$text_length_life_log2 <- log2(filtered_data_matched$text_length_live)


# calculate the p-value using a two-sample t-test
t_test_result <- t.test(text_length_log2 ~ sex, data = filtered_data_matched)

# Create a boxplot, that shows the mean as a blue cross and also shows the p-value on top




matched_data_text_length_2 <- ggplot(matched_data, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = text_length, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Text length (characters)", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')



matched_data_text_length_2



ggsave(here("visualisations", "matched_data_boxplot1.pdf"), plot = matched_data_text_length_2, width = 5, height = 6, units = "in", dpi = 600)

```

2.2. Text length life section
```{r warning=FALSE}
# Log2 transformation

filtered_data_matched <- matched_data

#Ersetze Werte kleiner als 60 in text_length_live mit NA im neuen DataFrame
filtered_data_matched$text_length_live[filtered_data_matched$text_length_live < 60] <- NA
filtered_data_matched$text_length_career[filtered_data_matched$text_length_career < 60] <- NA


filtered_data_matched$text_length_life_log2 <- log2(filtered_data_matched$text_length_live)


# Führe den t-Test mit den transformierten Daten durch
t_test_result <- t.test(text_length_life_log2 ~ sex, data = filtered_data_matched, na.action = na.exclude)



matched_text_length_life_2 <- ggplot(filtered_data_matched, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = text_length_live, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Text length, career section (characters)", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')

matched_text_length_life_2


ggsave(here("visualisations", "matched_data_boxplot2.pdf"), plot = matched_text_length_life_2, width = 5, height = 6, units = "in", dpi = 600)

```

2.3. Text length career section
```{r warning=FALSE}
# Log2 transformation

filtered_data_matched$text_length_career_log2 <- log2(filtered_data_matched$text_length_career)

# Führe den t-Test mit den transformierten Daten durch
t_test_result <- t.test(text_length_career_log2 ~ sex, data = filtered_data_matched, na.action = na.exclude)
# 



matched_text_length_career_2 <- ggplot(filtered_data_matched, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = text_length_career, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Text length career section (characters)", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')

matched_text_length_career_2


ggsave(here("visualisations", "matched_data_boxplot3.pdf"), plot = matched_text_length_career_2, width = 5, height = 6, units = "in", dpi = 600)
```

2.4. Number of links
```{r}

matched_data$number_of_links_log2 <- log2(matched_data$number_of_links)

# p-Wert aus einem T-Test für die Anzahl der Links berechnen
t_test_result <- t.test(number_of_links_log2 ~ sex, data = matched_data)

matched_data_links_2 <- ggplot(matched_data, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = number_of_links, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Number of links", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) +
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')


matched_data_links_2

# Plot speichern
ggsave(here("visualisations", "matched_data_boxplot4.pdf"), plot = matched_data_links_2, width = 5, height = 6, units = "in", dpi = 600)
```

2.5. Number of page edits
```{r}

# Log2 Transformation
# 
 matched_data$total_edits_log2 <- log2(matched_data$total_edits)

t_test_result <- t.test(total_edits_log2 ~ sex, data = matched_data)


 
 
matched_edits_2 <- ggplot(matched_data, aes(x = factor(sex, levels = c("female", "male"), labels = c("Women", "Men")), y = total_edits, fill = factor(sex, levels = c("female", "male")))) +
  geom_boxplot() +
    scale_fill_manual(values = c("female" = "#f4a582", "male" = "#92c5de")) + 
  labs(title = paste("Two-sample t-test, P-Value = ", round(t_test_result$p.value, 3), add_stars(t_test_result$p.value), sep = ""),
       x = "Gender", 
       y = "Number of edits", caption = "") +
  stat_summary(fun = mean, geom = "point", aes(group = sex),
               shape = 4, size = 3, color = "blue") + # Kreuz für den Mittelwert
   theme_minimal() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"), # Setzt den Hintergrund auf Weiß
    plot.background = element_rect(fill = "white", colour = NA),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Titel zentrieren und Größe anpassen
    plot.caption = element_text(hjust = 0.5, size = 16),
    axis.title.x = element_text(size = 16, , face = "bold"), # Größe des x-Achsentitels anpassen
    axis.title.y = element_text(size = 16, , face = "bold"), # Größe des y-Achsentitels anpassen
    axis.text.x = element_text(size = 16), # Größe des x-Achsentextes anpassen
    axis.text.y = element_text(size = 13)  # Größe des y-Achsentextes anpassen
  ) + 
  guides(fill = FALSE)+ 
  scale_y_continuous(trans = 'log2')


matched_edits_2

ggsave(here("visualisations", "matched_boxplot5.pdf"), plot =  matched_edits_2, width = 5, height = 6, units = "in", dpi = 600)

```


## Correlations

```{r, height = 5}
# select variables of interest as numeric variables
cor_data <- deu %>% select(total_edits, text_length, number_of_links,
                       total_service, total_traffic)

```





```{r, height = 5}
# calculate correlation matrix
COR <- cor(cor_data, method = "pearson")

COR

custom_labels <- c("Total Edits", "Text Lenght", "Number of Links", "Total Servise", "Total Page Traffic")

colnames(COR) <- custom_labels
rownames(COR) <- custom_labels


# plot
plot_cor <- corrplot(COR, method = "number", type = 'lower', bg = "grey", tl.col = "black", cl.pos = 'n', addgrid.col= "white")

pdf_file <- here("visualisations", "correlation.pdf")

# Save the plot as a PDF file
pdf(file = pdf_file)
corrplot(COR, method = "number", type = 'lower', bg = "grey", tl.col = "black", cl.pos = 'n', addgrid.col= "white")
dev.off()
```


table
```{r}
#calculate statstics with log scales

filtered_data_deu$text_length_career_log2 <- log2(filtered_data_deu$text_length_career)
filtered_data_deu$text_length_live_log2 <- log2(filtered_data_deu$text_length_live)
filtered_data_deu$text_length_log2 <- log2(filtered_data_deu$text_length)
filtered_data_deu$number_of_links_log2 <- log2(filtered_data_deu$number_of_links)
filtered_data_deu$total_edits_log2 <- log2(filtered_data_deu$total_edits)

filtered_data_matched$text_length_career_log2 <- log2(filtered_data_matched$text_length_career)
filtered_data_matched$text_length_live_log2 <- log2(filtered_data_matched$text_length_live)
filtered_data_matched$text_length_log2 <- log2(filtered_data_matched$text_length)
filtered_data_matched$number_of_links_log2 <- log2(filtered_data_matched$number_of_links)
filtered_data_matched$total_edits_log2 <- log2(filtered_data_matched$total_edits)


```



functions

```{r}



library(tibble)
calculate_statistics_log <- function(df) {
  # Initialisiere einen leeren DataFrame für die Ergebnisse
  ergebnisse <- tibble()

  for (variable in c("text_length_log2", "text_length_career_log2", "text_length_live_log2", "number_of_links_log2", "total_edits_log2")) {
    # Extrahiere die Daten für jede Gruppe
    data_male <- df %>%
      filter(sex == "male") %>%
      pull(variable)

    data_female <- df %>%
      filter(sex == "female") %>%
      pull(variable)

    # Überprüfe, ob die Variable im DataFrame existiert
    if (length(data_male) == 0 | length(data_female) == 0) {
      next
    }

    # Führe Welch-Test durch
    test <- t.test(data_male, data_female, na.action = na.exclude)

    # Berechne Cohen's d
    d <- cohen.d(data_male, data_female, na.rm = TRUE)$estimate

    # Füge Ergebnisse hinzu, Variablennamen ändern
    if (variable == "text_length_log2") {
      variable_name <- "Text length"
    } else if (variable == "text_length_career_log2") {
      variable_name <- "Text length, career section"
    } else if (variable == "text_length_live_log2") {
      variable_name <- "Text length, life section"
    } else if (variable == "number_of_links_log2") {
      variable_name <- "Number of links"
    } else if (variable == "total_edits_log2") {
      variable_name <- "Number of edits"
    }


    ergebnisse <- rbind(ergebnisse, tibble(
      Variable = variable_name,
      "Female Mean" = mean(data_female, na.rm = TRUE),
      "Male Mean" = mean(data_male, na.rm = TRUE),
      P_Value = test$p.value,
      "Effect size" = d
    ))
  }

  return(ergebnisse)
}



generate_and_save_table <- function(data, file_name) {
  # Funktion zur Formatierung der P-Werte innerhalb der übergeordneten Funktion, um den Scope zu begrenzen
  combine_p_value_and_stars <- function(p_value) {
    stars <- ifelse(p_value < .001, "***",
                    ifelse(p_value < .01, "**",
                           ifelse(p_value < .05, "*",
                                  ifelse(p_value < .1, ".", "ns"))))

    formatted_p_value <- format(round(p_value, 3), nsmall = 3)  # Format p-value with 3 digits

    if(grepl("\\*", stars)) {
      return(sprintf("<b>%s%s</b>", formatted_p_value, stars))
    } else {
      return(formatted_p_value)
    }
  }

  # P-Werte formatieren
  data$P_Value <- sapply(data$P_Value, combine_p_value_and_stars)

  # Datensatz vorbereiten
  data <- data %>%
    select(everything()) %>%
    mutate(across(where(is.numeric), round, digits = 3))

  # Tabelle erstellen
  descriptive_table <- kable(data, "html", escape = FALSE) %>%
    kable_styling("striped", full_width = F) %>%
    collapse_rows(columns = 1, valign = "top")#%>%
    save_kable(descriptive_table, file = here("visualisations", paste0(file_name, ".png")))

  return(descriptive_table)
}


```

apply functions
```{r}




#unmatched data
descriptives_deu <- calculate_statistics_log(filtered_data_deu)
#descriptives_deu$subgroup <- "whole sample"
generate_and_save_table(descriptives_deu, "deu_descriptives")


#matched data
descriptives_matched <- calculate_statistics_log(filtered_data_matched)
#descriptives_matched$subgroup <- "matched sample"
generate_and_save_table(descriptives_matched, "matched_descriptives")



```




